\begin{thebibliography}{99}
\bibitem{NTRU} Hoffstein, J., Pipher, J., Silverman, J.H.: \emph{NTRU: a ring-based public key cryptosystem}\needtodo{Publisher and Year}

\bibitem{Galteland} Herman Galteland, \emph{Fully Homomorphic Encryption Schemes}, 2015, Master Thesis, NTNU\needtodo{Year and published(?)}

\bibitem{Gentry} Gentry C., \textit{Fully Homomorphic Encryption Using Ideal Lattices}, Proceedings of the forty-first annual ACM symposium on Theory of computing p. 169-178, 2009

\bibitem{Short Sticleberg} Cramer R., Ducas L., Wesolowski B. (2017) Short Stickelberger Class Relations and Application to Ideal-SVP. In: Coron JS., Nielsen J. (eds) Advances in Cryptology – EUROCRYPT 2017. Lecture Notes in Computer Science, vol 10210. Springer-Verlag, Cham \improvement{Springer is Springer-Verlag?}

\bibitem{Recover Short Gen} Cramer R., Ducas L., Peikert C., Regev O. \emph{Recovering Short Generators of Principal Ideals in Cyclotomic Rings} Advances in Cryptography - EUROCRYPT 2016 II p. 550, Springer-Verlag

URL: \url{https://eprint.iacr.org/2015/313.pdf}

\bibitem{Recover2}
Espitau, T. et. al. \emph{Computing generator in cyclotomic integer rings}, EUROCRYPT 2016 I, Springer\needtodo{Make sure this is right source}

URL: \url{https://eprint.iacr.org/2016/957.pdf}

\bibitem{Reduction PG-PIP LWE} Peikert, C., \emph{Public-Key Cryptosystems from the
Worst-Case Shortest Vector Problem} [PUBLISHED BY?]

URL: \url{http://people.csail.mit.edu/cpeikert/pubs/svpcrypto.pdf}

\bibitem{Ajtai}  Ajtai, M., \emph{Generating hard instances of lattice problems} Quaderni di Matematica 2004

\url{URL: http://www.aracneeditrice.it/pdf/9788879994132.pdf}

\bibitem{Peikert Reduction} Peikert, C., \emph{Public-Key Cryptosystems from the Worst-Case Shortest Vector Problem}

\url{URL: https://web.eecs.umich.edu/~cpeikert/pubs/svpcrypto.pdf}

\bibitem{Intro To Cyclotomic Fields} Washington, L.C., \emph{Introduction to Cyclotomic Fields}, Graduate Texts in Mathematics,
vol. 83. Springer-Verlag, New York, 1st edition 1982

\bibitem{Prime Discriminant Division Theorem}
URL: \url{http://www.math.uconn.edu/~kconrad/blurbs/gradnumthy/disc.pdf}

\bibitem{Classic Recover}
URL: \url{https://arxiv.org/abs/1503.03107}

\bibitem{Lattice Beginner} Chi, D., et. al. \emph{Lattice Based Cryptography for Beginners}  URL: \url{https://eprint.iacr.org/2015/938.pdf}

\bibitem{Gjorsteen Lattice Intro} Gjørsteen, K., \emph{Lattice-Based Cryptography} \\URL \url{https://wiki.math.ntnu.no/_media/tma4160/lattice-i.pdf}:

\bibitem{Estimate Security} Rückert, M., Schneider, M., \emph{Estimating the Security of Lattice-based Cryptosystems} URL: \url{https://eprint.iacr.org/2010/137.pdf}

\bibitem{Basic Algebraic Number Theory} Oggier, F., \emph{Introduction to Algebraic Number Theory}, lecture notes given at NTU from January to April 2009 and 2010. URL \url{http://www1.spms.ntu.edu.sg/~frederique/ANT10.pdf}

\bibitem{Find Generator Classic} Biasse, J., Fieker, C. (2014). \emph{Subexponential class group and unit group computation in large degree number fields}. LMS Journal of Computation and Mathematics, 17(A), 385-403. URL: \url{https://www.cambridge.org/core/services/aop-cambridge-core/content/view/S1461157014000345}

\bibitem{Find Generator Quantum} Biasse, J.-F., Groves, M., \emph{A polynomial time quantum algorithm for computing class groups and solving the principal ideal problem in arbitrary degree number fields}\improvement{Different name some places}, In SODA 2016.

\bibitem{Compact Representation} Tiel, C., \emph{Short Proofs Using Compact Representations of Algebraic Integers}, Journal of Complexity p.310-329 Volume 11 Issue 3, 1995

\bibitem{Find Generator Quantum 2} Biasse, Song, \emph{On the quantum attacks against schemes relying on the hardness of finding a short generator of an ideal in \(\QQ(\zeta_{p^n})\)}, URL: \url{http://cacr.uwaterloo.ca/techreports/2015/cacr2015-12.pdf}

\bibitem{First R-LWE} Vadim Lyubashevsky, Christ Peikert, Oded Regev, \emph{On Ideal Lattices and Learning with Errors Over Rings}, EUROCRYPT 2010: 1-23

\bibitem{How Not To RLWE} Peikert C. (2016) How (Not) to Instantiate Ring-LWE. In: Zikas V., De Prisco R. (eds) Security and Cryptography for Networks. SCN 2016. Lecture Notes in Computer Science, vol 9841. Springer, Cham

\bibitem{Ideal Lattice Proof} Lyubashevsky, V., Miccianicio, D., \emph{Generalized compact knapsacks are collision resistant}, full version.\\
\url{https://pdfs.semanticscholar.org/a406/d27a16be28b858a36ba16ac7a72316177691.pdf}

\bibitem{Reg05} Regev, O., \emph{On Lattices, Learning with Errors, Random Linear Codes, and Cryptography}, STOC 2005 p. 84-93\\
URL: \url{https://dl.acm.org/citation.cfm?doid=1060590.1060603}

\bibitem{Smoothing Parameter Proof} Micciancio, D., Regev, O., \emph{Worst-case to average-case reductions based on Gaussian measures}\change{fix this reference}\\\url{https://cims.nyu.edu/~regev/papers/average.pdf}

\bibitem{Identifying Ideal Lattices} Ding, J., Lindner, R., \emph{Identifying Ideal Lattices}\change{find publisher} \\\url{https://eprint.iacr.org/2007/322.pdf}

%_________________ATTACKS ON LWE_________________%
\bibitem{LWE Attack 1} Arora, S., Ge, R.: \emph{New algorithms for learning in presence of errors}. In: In: Aceto, L., Henzinger, M., Sgall, J. (eds.) ICALP 2011, Part I. LNCS, vol. 6755, pp. 403-415. Springer, Heidenlberg (2011).\improvement{Stolen source, read?}

\bibitem{LWE Attack 2} Blum, A., Kalai, A., Wasserman, H.: \emph{Noise-tolerant learning, the parity problem, and the statistical query model}. J. ACM \textbf{50}(4), 506-519 (2003)

\bibitem{Bound on Size of Sample from Gaussian} Banaszczyk, W., \emph{New bounds in some transference theorems in the geometry of numbers}, Matematische Annalen, 296(4):625-635, 1993\improvement{have not read}

\bibitem{Error Tweak} Peikert. C., \emph{Lattice Cryptography for the Internet} \\
URL: \url{https://web.eecs.umich.edu/~cpeikert/pubs/suite.pdf}

\end{thebibliography}